Viscous Transport in Eroding Porous Media

### 2019-08-22 docs/transport/erosion_transport.tex
add a new figure in transport paper

\begin{figure}[H]
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
%\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\center
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment_long}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
dispersion in 20 nearly touching bodies with respect to initial porosity
(37.68\%) and another six porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted line is a line
of best fit with slope 0.5742.}
\end{figure}

@@

>>>>

\begin{figure}[H]
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
%\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\center
\includegraphics*[width =0.55\linewidth]{./figs/20b_second_moment_long}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
dispersion in 20 nearly touching bodies with respect to initial porosity
(37.68\%) and another six porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted line is a line
of best fit with slope 0.5742.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
dispersion in 20 nearly touching bodies with respect to initial porosity
(30.67\%) and another seven porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted lines are lines
of best fit with slope 0.9194 (95\%), 0.8666 (85.17\%), 0.8682(75.10\%), 0.9087 (65.02\%), 
0.9054(55.08\%), 0.7234(45.03\%), 0.6895(35.05\%), and 0.9225(30.67\%).}
\end{figure}
